Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
codewords number -1

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{data_sizes}
\end{center}
\caption{\small{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a codeword or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $0$ (just initialization) to $500$ thousand. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns, except
for the dotted line (non random in the legend). In that case we took the
first $N$ samples in our dataset. The difference is only visible for small
training sets ($1$K).
%
FIXME: Can we kill the ``non-random'' line.  It doesn't really add anything.
}}
\label{fig:data_sizes}
\end{figure}

@@

The 25 most frequently used codewords in the test set are shown in
Figure \ref{fig:codes1}.  
The frequency of use of these codewords are shown in Figure \ref{fig:freqs}.
The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 1),
perfect fifth (codewords 2 and 3) and fourth intervals (codewords 4
and 7), and a
major and minor triads (codewords 6 and 5, respectively).  Many of the remaining
codewords correspond to common transitions from one chord to another,
\eg a transitions between major triads in codes 8 and 10 ( Cmaj
$\rightarrow$ Fmaj)% assuming that chroma 0 is C) 
and the reverse transition in code 22 (\ie Fmaj $\rightarrow$ Cmaj).
FIXME: Does this transition have a better name like ``relative x''?

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{data_sizes}
\end{center}
\caption{\small{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a codeword or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $0$ (just initialization) to $500$ thousand. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns.
}}
\label{fig:data_sizes}
\end{figure}

@@

The 25 most frequently used codewords in the test set are shown in
Figure \ref{fig:codes1}.  
The frequency of use of these codewords are shown in Figure \ref{fig:freqs}.
The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 0),
perfect fifth (codewords 1 and 2) and fourth intervals (codewords 3
and 6), and a
major and minor triads (codewords 5 and 4, respectively).  Many of the remaining
codewords correspond to common transitions from one chord to another,
\eg a transitions between major triads in codes 7 and 9 ( Cmaj
$\rightarrow$ Fmaj)% assuming that chroma 0 is C) 
and the reverse transition in code 21 (\ie Fmaj $\rightarrow$ Cmaj).
FIXME: Does this transition have a better name like ``relative x''?
